\problem
Point $O$ is the circumcenter and point $H$ is the orthocenter in an acute
nonisosceles triangle $ABC$.
Circle $\omega_A$ is symmetric to the circumcircle of $AOH$ with respect to
$AO$.
Circles $\omega_B$ and $\omega_C$ are defined similarly.
Prove that circles $\omega_A$, $\omega_B$ and $\omega_C$ have a common point,
which lies on the circumcircle of $ABC$.
\solution
Denote by $X$ the intersection point of the circumcircle of $ABC$ and
$\omega_A$, by $H_A$ and $H_B$ denote a points symmetric to $H$ with respect to
the midpoints of segments $OA$ and $OB$ respectively.
By oriented angle between to lines $\ell_1$ и $\ell_2$ we mean the angle in
which it is necessary to rotate the line $\ell_1$ to obtain the line parallel
to $\ell_2$.
We denote this oriented angle by $\angle (\ell_1, \ell_2)$.
Using the simplest properties of the orinted angles we get
$\angle(BX, OX) = \angle(BX, AX) + \angle(AX, OX)$.
Moreover $\angle(BX, AX) = \angle (BC, AC) = \angle (AH, BH)$, because the
points $A$, $B$, $C$, $X$ are cyclic and the oriented angle between the sides
of triangle is equal to the angle between corresponding altitudes.
Additionaly we get $\angle(AX, OX) = \angle(A H_A, O H_A) = \angle (OH, AH)$,
because $A$, $O$, $X$ and  $H_A$ are lying on $\omega_A$.
Thus,
\(
    \angle (BX, OX) = \angle (AH, BH) + \angle (OH, AH) =
    \angle (OH, BH) = \angle (B H_B, O H_B)
\).
Consequently the point $X$ is on $\omega_B$.
In the same way we get that $X$  is on $\omega_C$.
\par
\emph{Another solution.} 
Let us think that the circumcircle of the triangle $ABC$ is a unit circle at
the complex plane with center at the origin.
The names of all points we identify with corresponding complex numbers.
Then $H = A + B + C$, a point $H_A$ symmetric to $H$ with respect to the
midpoint of segment $OA$ can be calculated by formula $H_A = - B - C$.
Let $X$ be a point of intersection of $\omega_A$ and $\omega_B$.
The fact that $X \in \omega_A$ and $X \in \omega_B$ is equivalent to 
\[
    \frac{X - O}{X - A} : \frac{- B - C - O}{- B - C - A}
        \in {\mathbb R}
\mbox{ and }
    \frac{X - O}{X - B} : \frac{- A - C - O}{- C - A - B}
        \in {\mathbb R}
.\]
Deviding one ratio by another we obtain that the quantity
\[
    \frac{X - B}{X - A} : \frac{- C - B}{- C - A}
\]
is real.
Consequently the points $X$, $A$, $B$ and $-C$ are cyclic and so the point $X$
is lying on the circumcirle of $ABC$ and different with $A$, $B$ and $C$.
And so we ontain the required.
\endproblem
% $problem-source: Ф.\,Бахарев, inspired by Iran TST 2013
